A spatio-temporal analysis of the environmental correlates of COVID-19 incidence in Spain

### 2020-05-06 Environmental-Correlates-of-COVID19-Spain/Environmental-Correlates-of-COVID19-Spain-Title-Page.tex
Final edits after discussion with co-authors, then resubmission to Geographical Analysis.

  \begin{abstract}
  Early in 2020 the novel SARS-CoV2 swept the globe, disrupting health
  systems and the economy. Public health interventions have slowed the
  spread of the virus, albeit at a high cost. How and when to ease
  restrictions to movement hinges in part on whether SARS-CoV2 will
  display seasonality due to variations in temperature, humidity, and
  hours of sunshine. Here, we address this by means of a spatio-temporal
  analysis of the incidence of COVID-19 in Spain. Use of spatial Seemingly
  Unrelated Regressions (SUR) allows us to model the incidence of reported
  cases of the disease per 100,000 population as an interregional
  contagion process, in addition to a function of temperature, humidity,
  and sunshine. In the analysis we also control for GDP per capita,
  percentage of older adults in the population, population density, and
  presence of mass transit systems. The results support the hypothesis
  that incidence of the disease is lower at higher temperatures and higher
  levels of humidity. Sunshine, in contrast, displays a positive
  association with incidence of the disease. Our control variables also
  yield interesting insights. Higher incidence is associated with higher
  GDP per capita and presence of mass transit systems in the province; in
  contrast, population density and percentage of older adults display
  negative associations with incidence of COVID-19.
  \end{abstract}

>>>>

  \begin{abstract}
  The novel SARS-CoV2 has disrupted health systems and the economy and
  public health interventions to slow its spread have been costly. How and
  when to ease restrictions to movement hinges in part on whether
  SARS-CoV2 will display seasonality due to variations in temperature,
  humidity, and hours of sunshine. Here, we address this question by means
  of a spatio-temporal analysis in Spain of the incidence of COVID-19, the
  disease caused by the virus. Use of spatial Seemingly Unrelated
  Regressions (SUR) allows us to model the incidence of reported cases of
  the disease per 100,000 population as an interregional contagion
  process, in addition to a function of temperature, humidity, and
  sunshine. In the analysis we also control for GDP per capita, percentage
  of older adults in the population, population density, and presence of
  mass transit systems. The results support the hypothesis that incidence
  of the disease is lower at higher temperatures and higher levels of
  humidity. Sunshine, in contrast, displays a positive association with
  incidence of the disease. Our control variables also yield interesting
  insights. Higher incidence is associated with higher GDP per capita and
  presence of mass transit systems in the province; in contrast,
  population density and percentage of older adults display negative
  associations with incidence of COVID-19.
  \end{abstract}
